Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-06-20 paper.tex
Add experimental results for grasping problem.

\begin{figure}[h]
\centering
\begin{minipage}[c]{0.6\linewidth}
\begin{tikzpicture}[y=0.55pt, x=0.55pt,yscale=-1, inner sep=0pt, outer sep=0pt]
\definecolor{dg}{rgb}{0,0.3,0}
\path[draw=black,line join=miter,line cap=butt,line width=0.800pt, fill=gray]
  (231.3249,143.2249) .. controls (178.0814,153.1889) and (178.5527,172.4247) ..
  (180.8173,200.8036) .. controls (183.2959,231.8645) and (195.6610,188.6038) ..
  (256.5787,230.0980) .. controls (295.8993,256.8813) and (346.4296,308.3911) ..
  (295.9747,178.5802) .. controls (275.5517,126.0356) and (304.8066,129.4735) ..
  (231.3249,143.2249) -- cycle;
\node at (230,180) {Obstacle};
\path[dashed,draw=dg,line join=miter,line cap=butt,line width=1.5pt]
  (88.8934,277.5752) .. controls (196.3490,276.5363) and (532.8532,213.7494) ..
(434.3656,81.6056) node [above = 0.1cm, color=dg, text width=1.8cm] {\small{Constrained manifold $\mathcal{M}$}};
\node [draw,circle,inner sep=2pt,fill = gray] (qn) at (97,277) {};
\node [above = 0.15cm] at (qn) {$q_{near}$};
\node [draw,circle,inner sep=2pt] (qr1) at (367,99) {};
\node [left = 0.2cm] at (qr1) {$q_{rand}$};
\draw [dashed,thin] (qn) -- (450,277);
\node [draw,circle,inner sep=2pt] (qr2) at (367,277) {};
\node [below right = 0.1cm] at (qr2) {$q_{rand}'$};
\node [draw,circle,inner sep=2pt,fill = gray] (qr3) at (345,225) {};
\node [above = 0.22cm] at (qr3) {$q_{rand}''$} ;
\draw [dashed,thin] (qr1) -- (qr2) -- (qr3);
\node [draw,circle,inner sep=2pt,fill = gray] (qnew) at (270,250);
\node [above = 0.1cm, left = 0.2cm] at (qnew) {$q_{new}$};
%\draw [thick] (qn) -- (qnew);

@@

An experimental study, presented in  \cite{dalibard09}, showed that
in complex environments, randomized motion planners were faster than
collision avoiding local planners. Another benefit of using global motion
planning compared to local gradient descent is the ability to avoid local 
minima.

We present in Fig.~\ref{fig:wb-shelves} an illustration of 
the use of randomized motion planning 
on complex manipulation problems. The humanoid robot HRP-2 faces shelves. It has to: (i) grasp
a ball lying on a shelf, (ii) put it on a higher shelf, (iii) come back to a natural
rest configuration. The statically stable manifold on which the planning takes place is
defined by tasks constraining the robot feet and CoM. The goal of the first problem
is defined by a hand configuration task (position and orientation), and a gaze task
(the robot has to see the ball). The goal of the second problem is defined by a 
different hand configuration and the same gaze task,
and finally, the goal of the third problem is the rest configuration.
Extension 1 presents a video of this motion.

@@

The motion presented in Fig.~\ref{fig:wb-shelves} looks very complicated.
The reasons are that the environment is complex and HRP-2 kinematic tree is highly constrained.
The motion has been optimized based on these constraints. Note that the
accessibility space of this robot is not wide enough to accomplish this task further 
away from the shelves, which could have eased the motion. One possibility to extend the
robot accessibility space is to automatically change the support polygon durint the motion to solve the task.
This is an ongoing research field, \cite{OussamaKanoun06102010} proposes some 
local solutions. This has not been integrated in our global planning algorithm yet.

>>>>

\begin{figure}[h]
\centering
\begin{minipage}[c]{0.6\linewidth}
\begin{tikzpicture}[y=0.55pt, x=0.55pt,yscale=-1, inner sep=0pt, outer sep=0pt]
\definecolor{dg}{rgb}{0,0.3,0}
\path[draw=black,line join=miter,line cap=butt,line width=0.800pt, fill=gray]
  (231.3249,143.2249) .. controls (178.0814,153.1889) and (178.5527,172.4247) ..
  (180.8173,200.8036) .. controls (183.2959,231.8645) and (195.6610,188.6038) ..
  (256.5787,230.0980) .. controls (295.8993,256.8813) and (346.4296,308.3911) ..
  (295.9747,178.5802) .. controls (275.5517,126.0356) and (304.8066,129.4735) ..
  (231.3249,143.2249) -- cycle;
\node at (230,180) {Obstacle};
\path[dashed,draw=dg,line join=miter,line cap=butt,line width=1.5pt]
  (88.8934,277.5752) .. controls (196.3490,276.5363) and (532.8532,213.7494) ..
(434.3656,81.6056) node [above = 0.1cm, color=dg, text width=1.8cm] {\small{Constrained manifold $\mathcal{M}$}};
\node [draw,circle,inner sep=2pt,fill = gray] (qn) at (97,277) {};
\node [above = 0.15cm] at (qn) {$q_{near}$};
\node [draw,circle,inner sep=2pt] (qr1) at (367,99) {};
\node [left = 0.2cm] at (qr1) {$q_{rand}$};
\draw [dashed,thin] (qn) -- (450,277);
\node [draw,circle,inner sep=2pt] (qr2) at (367,277) {};
\node [below right = 0.1cm] at (qr2) {$q_{rand}'$};
\node [draw,circle,inner sep=2pt,fill = gray] (qr3) at (345,225) {};
\node [above = 0.22cm] at (qr3) {$q_{rand}''$} ;
\draw [dashed,thin] (qr1) -- (qr2) -- (qr3);
\node [draw,circle,inner sep=2pt,fill = gray] (qnew) at (270,250) {};
\node [above = 0.1cm, left = 0.2cm] at (qnew) {$q_{new}$};
%\draw [thick] (qn) -- (qnew);

@@

We present in Fig.~\ref{fig:wb-shelves} an illustration of 
the use of randomized motion planning 
on complex manipulation problems. The humanoid robot HRP-2 faces shelves. It has to: (i) grasp
a ball lying on a shelf, (ii) put it on a higher shelf, (iii) come back to a natural
rest configuration. The statically stable manifold on which the planning takes place is
defined by tasks constraining the robot feet and CoM. The goal of the first problem
is defined by a hand configuration task (3 positions and 2 orientations), and a gaze task
(the robot has to look at the ball). The goal of the second problem is defined by a 
different hand configuration and the gaze task.
Finally, the goal of the third problem is the rest configuration.

For the two reaching motions, we generate 8 random goal configurations (Section~\ref{sec:goal-sampling}).

The result of RRT is optimized in two steps (see~\cite{dalibard09} for details):
\begin{enumerate}
\item the path is extended in order to move the final posture closer to the rest posture,
\item the path is optimized by random short-cuts.
\end{enumerate}

Extension 1 presents a video of this motion.

@@

We have run this set of motion planning problems 20 times. The results are compiled in Table~\ref{table:reaching}. We can notice that optimization dominates the total time of computation. This suggests that improvement can be easily achieved by using numerical optimization techniques. This is on-going work.
\begin{table}
\begin{tabular}{lrrr}
& min & max & average \\
number of nodes & 43.00 & 481.00 & 102.70 \\
goal generation time (seconds) \hspace {1cm} & 1.00 & 1.56 & 1.22 \\
planning time (seconds)& 67.36 & 376.84 & 134.28 \\
optimization time (seconds) & 204.22 & 671.26 & 521.47 \\
total times (seconds) & 468.23 & 864.68 & 656.97
\end{tabular}
\caption {Experimental results on 20 runs: 3 motion planning problems and 2 goal generations.}
\label{table:reaching}
\end{table}

Among all calls to \texttt{constraint-solver}, the average number of iterations is 6.5 and the success rate is above 95 percent.
